Manuscript title here

### 2024-09-11 manuscript.Rmd
test

  (4  Kliniskt för att förbättra omhändertagande används OFI
    Förklara vad OFI är för något
      To be able to asses and improve the quality of trauma care, improvement programmes aim to identify opportunities for improvements(OFI). OFI is multidiciplinary morbidity and mortality reviews, where oppertunity for improvemetns are identified in the structure and clinical process of trauma care(Hussein).)

>>>>

  (4  Kliniskt för att förbättra omhändertagande används OFI
    Förklara vad OFI är för något
      To be able to asses and improve the quality of trauma care, improvement programmes aim to identify opportunities for improvements(OFI). OFI is multidiciplinary morbidity and mortality reviews, where opportunity for improvements are identified in the structure and clinical process of trauma care[@albaaj_patient_2023].)
